TODO: A Survey of StarCraft AI Techniques

### 2012-05-24 survey.tex
some progress in competition section (more to come)

{\color{magenta}

@@

An initial attempt to run a StarCraft tournament at the Computational
Intelligence in Games conference 2010 suffered from technical problems.
These mainly stemmed from the desire to use evolved, largely untested
maps which proved to look interesting but made the submitted bots crash
so often that it would have been unjustifiable to announce a winner.

At the CIG 2011, the tournament was therefore run with a (secret) selection
of maps used in league play. It was organized by Tobias Mahlmann and Mike
Preuss and attracted 10 bots.

\begin{table*}[htb]
\caption{Bracket A results at CIG 2011, 
qualified for the final round: UAlbertaBot and Skynet.}
\label{tab:correlations}
\begin{small}
\begin{center}
\begin{tabular}{|l|c|c|c|}
\hline
Crashes & games & bot	& wins\\ \hline
0 &	 40 &	 UAlbertaBot &	 33\\
1 &   40 &	 Skynet	  &  31\\
2 &	 40 &	 AIUR	  &  24\\
1 &	 40 &	 Nova	  &  8\\
0 &	 40 &	 LSAI	  &  4\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table*}

Bracket B

Crashes	 Games	 Bot	 Wins
12	 40	 Xelnaga	 25
3	 40	 BroodwarBotQ	 23
0	 40	 BTHAI	 23
17	 40	 Protoss Beast Jelly	 17
0	 40	 EvoBot	 12
As BroodwarBotQ and BTHAI have the same number of wins, their direct encounter is evaluated which accounted 6 : 4 for the BroodwarBotQ.

Qualified for the final round: Xelnaga and BroodwarBotQ. Note that all qualified bots play Protoss.
Maps used for the first round: (2)MatchPoint 1.3, (4)Fighting Spirit 1.3, iCCupdestination 1.1, iCCup gaia, iCCup great barrier reef

>>>>

{\color{violet}

In order to inject new AI code into the StarCraft game, all recent
tournaments attached to scientific conferences employ the 
Brood War Application Programming Interface 
(BWAPI)\footnote{\url{http://code.google.com/p/bwapi/}} which 
enables replacing the human player interface with a C++ library,
some auxiliary libraries and the bot code. A consequence of this
indirect way of integrating new bots is that every machine can
only run one custom bot, requiring two computers for a 2-player game.

\subsection{AIIDE}
\label{sec:AIIDE}
this is left empty for now

@@

An initial attempt to run a StarCraft tournament at the Computational
Intelligence in Games conference 2010 suffered from technical problems.
These mainly stemmed from the desire to use evolved, largely untested
maps which proved to look interesting but made the submitted bots 
(and/or the Broodwar Terrain Analyzer (BWTA) provided with the BWapi interface) crash
so frequently that it would have been unjustifiable to announce a winner.

At CIG 2011, the tournament was therefore run with a (secret) selection
of maps used in league play. It was organized by Tobias Mahlmann and Mike
Preuss and attracted 10 bots. In addition to the ones discussed in previous
sections (UAlbertaBot, Skynet, AIUR, Nova, BroodwarBotQ, BTHAI), 
the set also contained LSAI, Xelnaga, Protoss Beast Jelly, and EvoBot,
these are shortly described in the following:

\paragraph*{LSAI (Zerg)} utilizes a heavily modified BWSAL to divide management
 of the units to different modules that communicate via a centralized information
 module. It works using a simple reactive strategy to try and survive early game
 attacks and macro up to a larger attack force and maintain map control.

\paragraph*{Xelnaga (Protoss)} is a modification of the AIUR bot that chooses the 
Dark Templar Opening in order to destroy the enemy base before defenses against
invisible units are available.

\paragraph*{Protoss Beast Jelly (Protoss)}

\paragraph*{EvoBot (Terran)} employs an evolutionary algorithm for obtaining rational
 unit combinations and influence map techniques for deciding the strategic locations. Note
 that this bot was submitted in a very early version, with many of its designed features not
 yet fully ready.

\begin{table*}[htb]
\caption{Results of the first round at CIG 2011, held in two brackets.
Qualified for the final round: UAlbertaBot and Skynet (from A), Xelnaga
and BroodwarBotQ (from B, the latter by comparing direct encounters
with BTHAI of which 6:4 were won).}
\label{tab:correlations}
\begin{small}
\begin{center}
% bracket A
\begin{tabular}{|l|c|c|c|}
\hline
\multicolumn{4}{|c|}{Bracket A} \\ \hline
Crashes & games & bot	& wins\\ \hline
0 &	 40 &	 UAlbertaBot &	 33\\
1 &   40 &	 Skynet	  &  31\\
2 &	 40 &	 AIUR	  &  24\\
1 &	 40 &	 Nova	  &  8\\
0 &	 40 &	 LSAI	  &  4\\
\hline
\end{tabular}
% bracket B
\begin{tabular}{|l|c|c|c|}
\hline
\multicolumn{4}{|c|}{Bracket B} \\ \hline
Crashes & games & bot	& wins\\ \hline
12 &	 40 &	 Xelnaga &	 25\\
3 &   40 &	 BroodwarBotQ  &  23 (6)\\
0 &	 40 &	 BTHAI	  &  23 (4)\\
17 &	 40 &	 Protoss Beast Jelly  & 17\\
0 &	 40 &	 EvoBot	  &  12\\
\hline
\end{tabular}
\end{center}
\end{small}
\end{table*}

As BroodwarBotQ and BTHAI have the same number of wins, their direct encounter is evaluated which accounted 6 : 4 for the BroodwarBotQ.
Note that all qualified bots play Protoss.

Maps used for the first round: (2)MatchPoint 1.3, (4)Fighting Spirit 1.3, iCCupdestination 1.1, iCCup gaia, iCCup great barrier reef
